%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Julia Cluceru } & Email : \href{mailto:julia.cluceru@ucsf.edu}{julia.cluceru@ucsf.edu}\\
  & Mobile : +1-203-536-9771 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California}{San Francisco, California}
      {Ph.D. in Pharmaceutical Sciences and Pharmacogenomics}{Sept. 2015 -- July 2020 (exp)}
      \resumeSubheading
      {University of North Carolina}{Chapel Hill, NC}
      {B.A. Mathematics, B.A. Chemistry, GPA 3.53}{Sept. 2009 -- May 2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Academic Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Lupo Lab, UCSF}{Sab Francisco, CA}
      {Ph.D. Candidate}{April 2017 - Present}
      \resumeItemListStart
        \resumeItem{Advisor}
          {Asst. Professor in Residence, Janine Lupo, Ph.D., UCSF Department of Radiology and Biomedical Imaging}
        \resumeItem{Proposed Dissertation Title}
          {Proposed dissertation title: Multiparametric Magnetic Resonance Imaging to Predict Tumor Biology}
      \resumeItemListEnd

    \resumeSubheading
      {Bautch Lab, UNC-CH}{Chapel Hill, NC}
      {Undergraduate Research Assistant}{Sept. 2011 - Aug. 2013}
      \resumeItemListStart
        \resumeItem{Advisor}{Professor Victoria Bautch, Ph.D., Beverly Long Chapin Distinguished Professor and Chair of Biology}
        \resumeItem{Publications}
            \resumeItemListStart
                \resumeItem{Blood vessel anastomosis is spatially regulated by flt-1 during angiogenesis}
                    {Nesmith JE, Chappell JC, Cluceru JG, Bautch VL., Development. 2017 Mar 1;144(5):889-896.}
                \resumeItem{Flt-1 (VEGFR-1) coordinates discrete stages of blood vessel formation}
                    {Chappell JC, Cluceru JG, Nesmith JE, Mouillesseaux KP, Bradley VB, Hartland CM, Hashambhoy-Ramsay YL, Walpole J, Peirce SM, Mac Gabhann F, Bautch VL. Cardiovasc Res. 2016 Jul 1;111(1):84-93}
                \resumeItem{Agent-based model of angiogenesis simulates capillary sprout initiation in multicellular networks}
                    {Walpole J, Chappell JC, Cluceru JG, Mac Gabhann F, Bautch VL, Peirce SM., Integr Biol (Camb). 2015 Sep;7(9):987-97}
            \resumeItemListEnd
%        \resumeItem{Laboratory Skills}
%          {Stem cell culture, PCR, live imaging microscopy, gel electrophoresis, cell fractionation, distillation, titration, data collection and analysis}
      \resumeItemListEnd
    \resumeSubheading
      {McLaughlin Lab, UNC-CH}{Chapel Hill, NC}
      {Undergraduate Research Assistant}{Sept. 2010 - June 2011}
      \resumeItemListStart
        \resumeItem{Advisor}{Professor Richard McLaughlin, Ph.D., Chair of Mathematics}
        \resumeItem{Fluid dynamics research project}
          {Designed and filmed fluid dynamics experiments for support of the project "Settling dynamics of solid spheres in viscous stratified fluids: the entrainment dominated regime"}
      \resumeItemListEnd

    \resumeSubheading
      {McManus Lab, Columbia University}{Lamont-Doherty Earth Observatory, Palisades, NY}
      {NSF Research Experience for Undergraduates Fellowship}{Summer 2011}
      \resumeItemListStart
        \resumeItem{Advisor}
          {Professor Jerry F. McManus, Ph.D., Dept. of Geochemistry}
        \resumeItem{Particle dyanmics research project}
          {Researching the biochemical flux of particles settling on the ocean floor using oceanic cores derived from the Atlantic ocean. Discovered a major oceanic circulation change ~125kyr during a historic global warming period, informing prediction of future oceanic circulation changes due to global warming.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------TEACHING & LEADERSHIP-----------------
\section{Teaching Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tutor Corps}{San Francisco, CA}
      {Test Preparation and Academic Tutor}{Dec. 2015 - pres.}
      \resumeItemListStart
        \resumeItem{Mathematics}
          {Elementary math, algebra, geometry, pre-calculus, calculus, AP statistics, AP Calculus}
        \resumeItem{Science}
          {Elementary and middle school science, biology, chemistry, physics, AP Biology, AP Chemistry}
        \resumeItem{Test Preparation}
            {SAT Mathematics, ACT Mathematics, ACT Science, SSAT, SAT II Chemistry, SAT II Mathematics 1 \& 2} 
      \resumeItemListEnd
      
    \resumeSubheading
      {Drugs of the Central Nervous System, UCSF School of Pharmacy}{San Francisco, CA}
      {Teaching Assistant}{April 2017 - June 2017}
      \resumeItemListStart
        \resumeItem{Advisor}
          {Associate Professor Pamela England, Ph.D.}
        \resumeItem{Responsibilities}
            {Oversight of student-led presentations, grading assignments}
      \resumeItemListEnd
      
    \resumeSubheading
      {Greenwich Education Group}{Greenwich, CT}
      {Test Preparation and Academic Tutor}{Aug. 2014 - Sept. 2015}
      \resumeItemListStart
        \resumeItem{Mathematics}
          {Elementary math, algebra, geometry, pre-calculus, calculus, AP statistics, AP Calculus}
        \resumeItem{Science}
          {Elementary and middle school science, biology, chemistry, physics, AP Biology, AP Chemistry}
        \resumeItem{Test Preparation}
            {SAT Mathematics, ACT Mathematics, ACT Science, SSAT, SAT II Chemistry, SAT II Mathematics 1 \& 2} 
      \resumeItemListEnd
      
    \resumeSubheading
      {Freelance}{Madrid, Spain}
      {Academic Tutor}{Aug. 2013 - July. 2014}
      \resumeItemListStart
        \resumeItem{English As a Second Language}
          {Reinforced and taught bilingual school students science and math in English.}
      \resumeItemListEnd
      
   \resumeSubheading
      {Freelance}{Chapel Hill, NC; Stamford, CT}
      {Academic Tutor}{2006 - Sep 2013}
      \resumeItemListStart
        \resumeItem{Mathematics}
          {Elementary math, algebra, geometry, pre-calculus, calculus, AP statistics, AP Calculus}
        \resumeItem{Science}
          {Elementary and middle school science, biology, chemistry, physics, AP Biology, AP Chemistry}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------DISTINCTIONS-----------------
\section{Distinctions \& Honors}
  \resumeSubHeadingListStart
    \resumeSubItem{National Institute of General Medical Sciences Ruth L. Kirschstein National Research Service Award (NRSA) Predoctoral Institutional Research Training Grant (T32)}
      {Fellows receive 23,844.00 for research-related expenses. September 2017-September 2018}
    \resumeSubItem{Pi Mu Epsilon Math Honors society}
      {Inducted in 2013}
    \resumeItem{Dean's List}{Appeared on 7 out of 8 semesters at UNC-CH}
    \resumeSubItem{Test scores}
      {MCAT: 36 - 97th percentile; PCAT: 442 - 99th percentile; GRE: 166 - 94th percentile; SAT: 2260 - 99th percentile}
  \resumeSubHeadingListEnd


%--------SKILLS & TECHNIQUES------------
\section{Skills}
  \resumeSubHeadingListStart
%    \item{
%      \textbf{Programming Languages}{: R, python, Octave}
%      \hfill
%      \textbf{Technologies}{: Stem cell culture, PCR, live imaging microscopy, gel electrophoresis, cell fractionation, distillation, titration, data collection and analysis}
%    }
    \resumeSubItem{Programming Languages}{R, python, octave, bash, cshell, Linux environment}
    \resumeSubItem{Analysis}{Data wrangling, imputation, machine learning, applied statistics}
    \resumeSubItem{Mathematics}{Differential equations, multi-variable calculus, linear algebra}
    \resumeSubItem{Laboratory Technologies}{Stem cell culture, PCR, live imaging microscopy, gel electrophoresis, cell fractionation}
  \resumeSubHeadingListEnd

%--------PRESENTATIONS------------
\section{Presentations \& Posters}
  \resumeSubHeadingListStart
    \resumeItem{Nov. 2016}{Hidden secrets of bulk tissue: Understanding glioma through meta-analysis of transcriptional data. Quantitative Biosciences Consortium Retreat Poster Session}
    \resumeItem{Aug. 2011}{Piecing Together Ocean Circulation Changes: How the North Atlantic Circulation Changed from MIS 6 to MIS 5e. NSF REU Poster Session}
  \resumeSubHeadingListEnd

%--------CONFERENCES------------
\section{Conferences}
  \resumeSubHeadingListStart
    \resumeItem{March 2017}{International Society for Magnetic Resonance Imaging Machine Learning Workshop}
    {Asilomar Conference Grounds, Monterey, CA}
    \resumeItem{May. 2017}{Department of Radiology and Biomedical Imaging annual retreat}
    \resumeItem{Feb. 2017}{American Association of Pharmaceutical Sciences InSight Asia-Pacific Research Symposium}
    
    \resumeItem{Feb. 2016}{Immune checkpoint inhibition for Hypermutant GBM resulting from germline MMR deficiency. Quantitative Biosciences Consortium Journal Club}
    \resumeItem{Aug. 2011}{Piecing Together Ocean Circulation Changes: How the North Atlantic Circulation Changed from MIS 6 to MIS 5e. NSF REU Poster Session}
  \resumeSubHeadingListEnd
  
  
%--------VOLUNTEERING------------
%\section{Volunteering}
%  \resumeSubHeadingListStart
%    \resumeSubheading{Big Brothers & Big Sisters of America}{Chapel Hill, NC}{Big Sister}{Jan 2010 - May 2013}
%        \resumeSubItem{Volunteer}{Department of Radiology and Biomedical Imaging annual retreat}
%  \resumeSubHeadingListEnd
  
%--------VOLUNTEERING------------
%\section{Volunteering \& Professional Associations}
%    \resumeSubHeadingListStart
%        \resumeSubheading
%        {American Association of Pharmaceutical Science}{San Francisco, CA}
%        {Member}{Jan 2016 - pres.}
%        \resumeSubheading
%        {Big Brothers Big Sisters of America}{Chapel Hill, NC}
%        {Big Sister}{Jan 2010 - May 2013}
%            \resumeItemListStart
%                \resumeItem{Anaies Gibson}{Mentored and tutored Anaies for 3 years in all subjects.}
%                \resumeItem{Organizational support}{Organized BBBS of the Triangle meetings at the Campus Y}
%            \resumeItemListEnd
%        \resumeSubheading
%        {Alpha Chi Sigma}{Chapel Hill, NC}
%        {Brother}{Jan 2011 - May 2013}
%            \resumeItemListStart
%               \resumeItem{Professional Chemistry Fraternity}{Member}
%            \resumeItemListEnd
%        \resumeSubheading
        
 %   \resumeSubHeadingListEnd
    
    
\section{Leadership \& Professional Associations}    
    \resumeSubHeadingListStart
        \resumeSubheading
              {American Association of Pharmaceutical Sciences}{San Francisco, CA}
              {Member}{2016 - pres.}
        \resumeSubheading
              {International Society for Magnetic Resonance Imaging}{San Francisco, CA}
              {Trainee Member}{2017 - pres.}
        \resumeSubheading
            {Big Brothers Big Sisters of America}{Chapel Hill, NC}
            {Big Sister}{Jan 2010 - May 2013}
            \resumeItemListStart
                \resumeItem{Anaies Gibson}{Mentored and tutored Anaies for 3 years in all subjects}
                \resumeItem{Organizational support}{Organized BBBS of the Triangle meetings at the Campus Y}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
